Embedding intuitionistic into classical logic

### 2022-08-01 Notes/Embedding intuitionistic into classical logic/EIICL.tex
First fully working implementation of the translation (single-file only)

\usepackage{amsmath,amssymb,amsthm}
\usepackage{ wasysym }
\usepackage{ stmaryrd }
\usepackage{ mathpartir }
\usepackage{bussproofs}
\usepackage{enumerate}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{arrows,shapes,quotes}
\usepackage{stackengine}
\usepackage{bbold}
\usepackage{footmisc}

@@

@@

	The idea is to encode the Kripke semantics of intuitionistic logic classically and is quite close to what was done in~\cite{iemhoff2010eskolemization}. We first present an embedding from IPC to CQC which is conceptually easier to understand, but will then reduce it to CPC.

@@

	\begin{definition}
		Let $\varphi$ be a propositional formula. Define $\varphi^{k}$ inductively as follows:
		\begin{itemize}
			\item $A^{k} = A(k)$ for every propositional variable $A$.
			\item $(\varphi\wedge\psi)^k = \varphi^k\wedge\psi^k$.
			\item $(\varphi\vee\psi)^k = \varphi^k\vee\psi^k$.
			\item $(\varphi\to \psi)^k = \forall u(k\preceq u\to\varphi^{u}\to\psi^{u})$ where $u$ is some new free variable.
		\end{itemize}
		Let $K(\varphi)$ encode that $\preceq$ is a partial order, the persistency condition for all propositional variables occurring in $\varphi$
		\begin{align*}
			K(\varphi) = &\forall k(k\preceq k)\wedge \forall k\forall l(k\preceq l\to l\preceq k\to l = k) \wedge \\&\forall k\forall l\forall m(k\preceq l \to l\preceq m\to k\preceq m)\wedge\\&\bigwedge \{\forall k\forall l(k\preceq l\to A(k)\to A(l))\:|\: \text{ $A$ occurs in $\varphi$}\}
		\end{align*}
		Then define
		$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
		where $u$ is some free variable.
	\end{definition}

	All that we have done is model Kripke frames with a finite number of propositional variables as a first-order theory and by definition we have

@@

	\subsection{Quantifiers in Classical Logic}

	Of course translating a propositional formula to a first-order formula is somewhat unsatisfying. As a first step to obtaining a propositional formula we wish to eliminate the quantifiers. Since we are interested in preserving validity we use Herbrandization. In this process we introduce free variables and also additional function symbols to the signature. Whenever we speak of a new free variable what is meant is a free variable that does not occur in any of the considered formulas. Whenever a new function symbol is introduced we implicitly extend the signature by some not previously contained symbol.

	Now usually in classical logic before removing quantifiers prenexification is performed, however since we wish to apply a similar procedure to intuitionistic logic later, where prenexification is not valid, we will do without.

	\begin{definition}
		For formulas $\varphi$ we define the Skolemization $\varphi^S_T$ and Herbrandization $\varphi^H_T$ with respect to $T$ by simultaneous induction as follows:
		\begin{itemize}
			\item $A^S_T = A^H_T = A$ for each atomic $A$.
			\item $(\varphi\circ\psi)^X_T = \varphi^X_T\circ\psi^X_T$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
			\item $(\varphi\to\psi)^S_T = \varphi^H_T\to \psi^S_T$\\$(\varphi\to\psi)^H_T = \varphi^S_T\to\psi^H_T$.
			\item $(\forall x\varphi)^S_T = \forall x(\varphi[a/x]^S_{T\cup\{a\}}[x/a])$ where $a$ is a new free variable\\$(\forall x\varphi)^H_T = \varphi[s(t_1,\dots,t_n)/x]^H_T$ where $s$ is a new function, $\{t_1\dots t_n\} = T$.
			\item $(\exists x\varphi)^S_T = \varphi[s(t_1,\dots,t_n)/x]^S_T$ where $s$ is a new function, $\{t_1\dots t_n\} = T$\\$(\exists x\varphi)^H_T = \exists x(\varphi[a/x]^H_{T\cup\{a\}}[x/a])$ where $a$ is a new free variable.
		\end{itemize}
		Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
	\end{definition}

	\begin{theorem}For every formula $\varphi$
		\begin{itemize}
			\item $\varphi$ and $\varphi^S$ are classically equisatisfiable.
			\item $\varphi$ and $\varphi^H$ are classically equivalid.
		\end{itemize}
	\end{theorem}

	which follows from the following two Lemmata:

	\begin{lemma}
		Let $\chi$ be a formula and $\{t_1\dots t_n\} = T$ contain all free variables in $\chi$, then for every structure $\mathcal M = (M, I)$ there exists $\mathcal M_\chi = (M, I_\chi$) such that $p^{I_{\chi}} = p^I$ for all function and relation symbols $p$ occurring in $\chi$ and for all variable assignments $v$ we have
		\begin{itemize}
			\item if $\mathcal M, v\models\chi$ then $\mathcal M_\chi, v\models\chi^S_T$.
			\item if $\mathcal M, v\not\models\chi$ then $\mathcal M_\chi, v\not\models\chi^H_T$.
		\end{itemize}
	\end{lemma}

		1. $\chi = \varphi\circ\psi$ for $\circ\in\{\wedge,\vee,\to\}$. By induction hypothesis there exist $\mathcal M_{\varphi, v} = (M, I_{\varphi, v}), \mathcal M_{\psi, v} = (M, I_{\psi, v})$ for $\varphi,\psi$ as in the lemma. Then we can define $I_{\chi, v}$ as follows:

		For every symbol $p$ that occurs in $\varphi^S$ or $\varphi^H$ but not $\psi^S, \psi^H$ have $p^{I_{\chi, v}} = p^{I_{\varphi, v}}$. For every symbol $p$ that occurs in $\psi^S$ or $\psi^H$ but not $\varphi^S, \varphi^H$ have $p^{I_{\chi, v}} = p^{I_{\psi, v}}$. Otherwise $p$ already occurs in $\varphi$ so have $p^{I_{\chi, v}} = p^I$.

		Let $\circ=\to$. Suppose $\mathcal M, v\models\chi$. Then $\mathcal M, v\not\models\varphi$ or $\mathcal M\models\psi$ and therefore $\mathcal M_\chi\not\models\varphi^S_T$ or $\mathcal M_\chi\models\psi^H_T$, i.e. $\mathcal M_\chi\models\chi^S_T$. On the other hand suppose $\mathcal M, v\not\models\chi$. Then $\mathcal M, v\models\varphi$ and $\mathcal M, v\not\models\psi$ and therefore $\mathcal M_\chi, v\models \varphi^S_T$ and $\mathcal M_\chi, v\not\models\psi^S_T$, i.e. $\mathcal M_\chi\not\models\chi^H_T$. Analogous arguments work for $\circ\in\{\wedge, \vee\}$.

		2. $\chi = \forall x\varphi$. Choose $s^{I_\chi}:M^n\to M$ such that $s^{I_\chi}(x_1,\dots, x_n) = m$ if there exists $m\in M$ such that $\mathcal M, v[x_1/t_1\dots x_n/t_n, m/a]\not\models\varphi[a/x]$ for all $v$ and arbitrary otherwise. Since $T$ contains all free variables occurring in $\chi$ this is a well-defined function.

		By induction hypothesis there exists a structure $\mathcal M_{\varphi[a/x]}$ as is the Lemma. Let $p^{I_\chi} = p^{I_{\varphi[a/x]}}$ for all symbols occurring in $\chi$ and $$p^{I_\chi}(x_1\dots x_{i-1}, x_{i+1}\dots x_m) = p^{I_{\varphi[a/x]}}(x_1\dots x_{i-1}, s^{I_\chi}(x_1\dots x_n), x_{i+1}\dots x_m)$$ for all symbols $p$ occurring in $\varphi[a/x]^S_{T\cup a}$ or $\varphi[a/x]^H_{T\cup a}$ but not in $\chi$ where $x_i$ is the argument corresponding to the free variable $a$.

		Suppose $\mathcal M, v\models\chi$. Then for all $m\in M$ $\mathcal M, v[m/a]\models\varphi[a/x]$ and therefore $\mathcal M_{\chi}, v[m/a]\models\varphi[a/x]^S_{M\cup\{a\}}$ and thus $\mathcal M_{\chi}, v\models \forall x\varphi([a/x]^S_{M\cup\{a\}}[x/a])$, i.e. $\mathcal M_\chi,v\models \chi^S$. On the other hand suppose $\mathcal M, v\not\models\chi$. Then there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\varphi[a/x]$ and therefore $\mathcal M_\chi, v[m/a]\not\models\varphi[a/x]^H_{T\cup\{a\}}$ and so by definition $\mathcal M_\chi, v\not\models\varphi[s(t_1,\dots t_n)/x]^H_T$, i.e. $\mathcal M_\chi, v\not\models(\forall x\varphi)^H_T$.

		3. $\chi = \exists x\varphi$. The argument runs dually to 2. Choose $s^{I_\chi}:M^n\to M$ such that $s^{I_\chi}(x_1,\dots, x_n) = m$ if there exists $m\in M$ such that for all $v$ we have $\mathcal M, v[x_1/t_1\dots x_n/t_n, m/a]\models\varphi[a/x]$ and arbitrary otherwise. Since $T$ contains all free variables occurring in $\chi$ this is a well-defined function.

		By induction hypothesis there exists a structure $\mathcal M_{\varphi[a/x]}$ as is the Lemma. Let $p^{I_\chi} = p^{I_{\varphi[a/x]}}$ for all symbols occurring in $\chi$ and $$p^{I_\chi}(x_1\dots x_{i-1}, x_{i+1}\dots x_m) = p^{I_{\varphi[a/x]}}(x_1\dots x_{i-1}, s^{I_\chi}(x_1\dots x_n), x_{i+1}\dots x_m)$$ for all symbols $p$ occurring in $\varphi[a/x]^S_{T\cup a}$ or $\varphi[a/x]^H_{T\cup a}$ but not in $\chi$ where $x_i$ is the argument corresponding to the free variable $a$.

		Then as in 2 from $\mathcal M, v\models \chi$ follows $\mathcal M_\chi,v\models\chi^S_T$ and from $\mathcal M, v\not\models \chi$ follows $\mathcal M_\chi,v\not\models\chi^H_T$.
	\end{proof}

	\begin{lemma}
		For every structure $\mathcal M$ and $\{t_1\dots t_n\} = T$ that contains all free variables in $\chi$ and variable assignment $v$
		\begin{itemize}
			\item if $\mathcal M, v\models\varphi^S_T$ then $\mathcal M, v\models \varphi$
			\item if $\mathcal M, v\not\models\varphi^H_T$ then $\mathcal M, v\not\models\varphi$.
		\end{itemize}
	\end{lemma}

		1. $\chi = \varphi\to\psi$. Suppose $\mathcal M, v\models\chi^S_T$, i.e. $\mathcal M, v\not\models\varphi^H_T$ or $\mathcal M, v\models\psi^S_T$. By induction hypothesis $\mathcal M, v\not\models \varphi$ or $\mathcal M, v\models\psi$, i.e. $\mathcal M, v\models \chi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_T$, i.e. $\mathcal M, v\models\varphi^S_T$ and $\mathcal M, v\not\models\varphi^H_T$. Again by induction hypothesis $\mathcal M,v\models\varphi$ and $\mathcal M, v\not\models \varphi$, so $\mathcal M, v\not\models\chi$.

		4. $\chi = \forall x\varphi$.  Suppose $\mathcal M, v\models\chi^S_T$, i.e. for all $m\in M$ we have $\mathcal M, v[m/a]\models \chi[a/x]^S_{T\cup\{a\}}$ and by induction hypothesis $\mathcal M, v[m/a]\models \chi[a/x]$. Then it follows that $\mathcal M, v\models\varphi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_T$, i.e. there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\chi[a/x]^H_{T\cup \{a\}}$, then by induction hypothesis $\mathcal M, v[m/a]\not\models \chi[a/x]$, i.e. $\mathcal M, v\not\models\forall x\chi$.

	\section{Equivalid normalization}

>>>>

\usepackage{amsmath,amssymb,amsthm}
\usepackage{ wasysym }
\usepackage{ stmaryrd }
\usepackage{ mathpartir }
\usepackage{bussproofs}
\usepackage{enumerate}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{arrows,shapes,quotes}
\usepackage{stackengine}
\usepackage{bbold}
\usepackage{footmisc}
\usepackage{wrapfig}

@@

	\section{Skolemization and Herbrandization}

	An important step in the embedding will be the elimination of quantifiers via Herbrandization.
	In this process we introduce fresh variables and add additional function symbols to the signature.
	A fresh variable is any variable that does not occur in any of the considered formulas.
	Whenever we add a function symbol we implicitly extend the signature by some not previously contained symbol.

	\begin{definition}
		For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to $Z$ by simultaneous induction as follows:
		\begin{itemize}
			\item $A^S_Z = A^H_Z = A$ for each atomic $A$.
			\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
			\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$\\$(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
			\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
			\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.
		\end{itemize}
		Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
	\end{definition}

	\begin{theorem}
		\label{thm:herbrand-skolem}
		For every formula $\varphi$
		\begin{itemize}
			\item $\varphi$ and $\varphi^S$ are classically equisatisfiable.
			\item $\varphi$ and $\varphi^H$ are classically equivalid.
		\end{itemize}
	\end{theorem}
	which follows from the following two Lemmata:
	\begin{lemma}
		Let $\chi$ be a formula and let $\{z_1\dots z_n\} = Z$ contain all free variables in $\chi$, then for every structure $\mathcal M = (M, I)$ there exists $\mathcal M_\chi = (M, I_\chi$) such that $p^{I_{\chi}} = p^I$ for all function and relation symbols $p$ occurring in $\chi$ and for all variable assignments $v$ we have
		\begin{itemize}
			\item if $M, v \models\chi$ then $\mathcal M_\chi, v\models\chi^S_T$.
			\item if $\mathcal M, v\not\models\chi$ then $\mathcal M_\chi, v\not\models\chi^H_T$.
		\end{itemize}
	\end{lemma}

		1. $\chi = \varphi\circ\psi$ for $\circ\in\{\wedge,\vee,\to\}$. By induction hypothesis there exist $\mathcal M_{\varphi, v} = (M, I_{\varphi, v})$ and $\mathcal M_{\psi, v} = (M, I_{\psi, v})$ for $\varphi,\psi$ as stated in the lemma.
		Then we can define $I_{\chi, v}$ as follows:

		For every symbol $p$ that occurs in $\varphi^S_Z$ or $\varphi^H_Z$ but not $\psi^S_Z, \psi^H_Z$, we set $p^{I_{\chi, v}} = p^{I_{\varphi, v}}$. For every symbol $p$ that occurs in $\psi^S_Z$ or $\psi^H_Z$ but not $\varphi^S_Z, \varphi^H_Z$, we set $p^{I_{\chi, v}} = p^{I_{\psi, v}}$. Otherwise $p$ already occurs in $\varphi$ so have $p^{I_{\chi, v}} = p^I$.

		Let $\circ=\ \to$. Suppose $\mathcal M, v\models\chi$. Then $\mathcal M, v\not\models\varphi$ or $\mathcal M\models\psi$ and therefore $\mathcal M_\chi\not\models\varphi^S_Z$ or $\mathcal M_\chi\models\psi^H_Z$, i.e. $\mathcal M_\chi\models\chi^S_Z$. On the other hand suppose $\mathcal M, v\not\models\chi$. Then $\mathcal M, v\models\varphi$ and $\mathcal M, v\not\models\psi$ and therefore $\mathcal M_\chi, v\models \varphi^S_Z$ and $\mathcal M_\chi, v\not\models\psi^S_Z$, i.e. $\mathcal M_\chi\not\models\chi^H_Z$. Analogous arguments work for $\circ\in\{\wedge, \vee\}$.

		2. $\chi = \forall x\varphi$. Choose $s^{I_\chi}:M^n\to M$ such that $s^{I_\chi}(x_1,\dots, x_n) = m$ if there exists $m\in M$ such that $\mathcal M, v[x_1/z_1\dots x_n/z_n, m/a]\not\models\varphi[a/x]$ for all $v$ and arbitrary otherwise. Since $Z$ contains all free variables occurring in $\chi$ this is a well-defined function.

		By induction hypothesis there exists a structure $\mathcal M_{\varphi[a/x]}$ as is the Lemma. Let $p^{I_\chi} = p^{I_{\varphi[a/x]}}$ for all symbols occurring in $\chi$ and $$p^{I_\chi}(x_1\dots x_{i-1}, x_{i+1}\dots x_m) = p^{I_{\varphi[a/x]}}(x_1\dots x_{i-1}, s^{I_\chi}(x_1\dots x_n), x_{i+1}\dots x_m)$$ for all symbols $p$ occurring in $\varphi[a/x]^S_{Z\cup a}$ or $\varphi[a/x]^H_{Z\cup a}$ but not in $\chi$ where $x_i$ is the argument corresponding to the free variable $a$.

		Suppose $\mathcal M, v\models\chi$. Then, for all $m\in M$ we have that $\mathcal M, v[m/a]\models\varphi[a/x]$ and therefore $\mathcal M_{\chi}, v[m/a]\models\varphi[a/x]^S_{Z\cup\{a\}}$ and thus $\mathcal M_{\chi}, v\models \forall x\varphi([a/x]^S_{Z\cup\{a\}}[x/a])$, i.e. $\mathcal M_\chi,v\models \chi^S_Z$. On the other hand suppose $\mathcal M, v\not\models\chi$. Then there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\varphi[a/x]$ and therefore $\mathcal M_\chi, v[m/a]\not\models\varphi[a/x]^H_{Z\cup\{a\}}$ and so by definition $\mathcal M_\chi, v\not\models\varphi[s(z_1,\dots z_n)/x]^H_Z$, i.e. $\mathcal M_\chi, v\not\models(\forall x\varphi)^H_Z$.

		3. $\chi = \exists x\varphi$. The argument runs dually to 2. Choose $s^{I_\chi}:M^n\to M$ such that $s^{I_\chi}(x_1,\dots, x_n) = m$ if there exists $m\in M$ such that for all $v$ we have $\mathcal M, v[x_1/z_1\dots x_n/z_n, m/a]\models\varphi[a/x]$ and arbitrary otherwise. Since $Z$ contains all free variables occurring in $\chi$ this is a well-defined function.

		By induction hypothesis there exists a structure $\mathcal M_{\varphi[a/x]}$ as is the Lemma. Let $p^{I_\chi} = p^{I_{\varphi[a/x]}}$ for all symbols occurring in $\chi$ and $$p^{I_\chi}(x_1\dots x_{i-1}, x_{i+1}\dots x_m) = p^{I_{\varphi[a/x]}}(x_1\dots x_{i-1}, s^{I_\chi}(x_1\dots x_n), x_{i+1}\dots x_m)$$ for all symbols $p$ occurring in $\varphi[a/x]^S_{Z\cup a}$ or $\varphi[a/x]^H_{Z\cup a}$ but not in $\chi$ where $x_i$ is the argument corresponding to the free variable $a$.

		Then as in 2 from $\mathcal M, v\models \chi$ follows $\mathcal M_\chi,v\models\chi^S_Z$ and from $\mathcal M, v\not\models \chi$ follows $\mathcal M_\chi,v\not\models\chi^H_Z$.
	\end{proof}

	\begin{lemma}
		For every structure $\mathcal M$ and $\{z_1\dots z_n\} = Z$ that contains all free variables in $\chi$ and variable assignment $v$
		\begin{itemize}
			\item if $\mathcal M, v\models\varphi^S_Z$ then $\mathcal M, v\models \varphi$
			\item if $\mathcal M, v\not\models\varphi^H_Z$ then $\mathcal M, v\not\models\varphi$.
		\end{itemize}
	\end{lemma}

		1. $\chi = \varphi\to\psi$. Suppose $\mathcal M, v\models\chi^S_Z$, i.e. $\mathcal M, v\not\models\varphi^H_Z$ or $\mathcal M, v\models\psi^S_Z$. By induction hypothesis $\mathcal M, v\not\models \varphi$ or $\mathcal M, v\models\psi$, i.e. $\mathcal M, v\models \chi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_Z$, i.e. $\mathcal M, v\models\varphi^S_T$ and $\mathcal M, v\not\models\varphi^H_Z$. Again by induction hypothesis $\mathcal M,v\models\varphi$ and $\mathcal M, v\not\models \varphi$, so $\mathcal M, v\not\models\chi$.

		4. $\chi = \forall x\varphi$.  Suppose $\mathcal M, v\models\chi^S_Z$, i.e. for all $m\in M$ we have $\mathcal M, v[m/a]\models \chi[a/x]^S_{Z\cup\{a\}}$ and by induction hypothesis $\mathcal M, v[m/a]\models \chi[a/x]$. Then it follows that $\mathcal M, v\models\varphi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_Z$, i.e. there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\chi[a/x]^H_{Z\cup \{a\}}$, then by induction hypothesis $\mathcal M, v[m/a]\not\models \chi[a/x]$, i.e. $\mathcal M, v\not\models\forall x\chi$.

@@

	The idea is to encode the Kripke semantics of intuitionistic logic classically and is quite close to what was done in~\cite{iemhoff2010eskolemization}. We first present an embedding from IPC to CQC which is conceptually easier to understand, but will then reduce it to CPC. To that end we will first propose a Tseytin-like translation, that reduces formulas to a normal form while preserving validity:

	\begin{theorem}\label{thm:Tseytin}
		For every propositional formula $\varphi$ there effectively are an atom $P$ and a set of $\mathcal S$ of formulas (over an extended set of propositions) of one of the forms\\
		$\text{ \hspace{1cm}} A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$\\
		for atomic $A, B, C$, such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The time complexity of the transformation is linear in the input size.
	\end{theorem}

	\begin{theorem}
		Let $\mathcal S$ be a set of formulas of the form
		$$(A\wedge B)\to C, (A\vee B)\to C, A\to (B\wedge C), A\to(B\vee C), (A\to B)\to C$$
		and $\mathcal F_\to\subseteq\mathcal S$ denote the subset of formulas of the form $(A\to B)\to C$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including the following formulas:
		\begin{itemize}
			\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
			\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
			\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
			\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
		\end{itemize}
		Then, $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore, there is an effective procedure for translating counter-models between the sentences.
	\end{theorem}

@@

	\begin{definition}
		Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively as follows:
		\begin{itemize}
			\item $A^{u} = A(u)$ for every propositional variable $A$.
			\item $\bot^u = \bot$.
			\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
			\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
		\end{itemize}
		Let $K(\varphi)$ encode the theory of Kripke structures, i.e.
		$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
		with e.g.
		\begin{align*}
			\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
			\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w)\:|\: \text{ $A$ is a propositional variable that occurs in $\varphi$}\}
		\end{align*}
		Then define
		$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
		where $u$ is some free variable.
	\end{definition}

	\noindent As all we have done is modelling Kripke frames as a first-order theory we directly obtain:

@@

	\subsection{Normal form transformation}

	Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step towards obtaining a propositional formula we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. In fact our translation is often presented as the first step in the Tseytin transformation, after which the individual formulas are then converted to CNF.
	Hence, the propositional case of our translation is well known, but we are not aware of any work that uses just this step as a stand-alone. A similar translation for intuitionistic propositional logic was also proposed in~\cite{statman1979intuitionistic}.

	\begin{definition}
		Let $\varphi$ be some formula. For each subformula $\psi$ of $\varphi$, consider some new $n$-ary relation symbol $P_\psi$, where $n$ is the number of variables occurring in $\psi$ that is not quantified within $\psi$. We denote those variables with $\vec z_\psi$ in some arbitrary but fixed order. We inductively define clause sets $\mathcal S^+(\varphi)$ and $\mathcal S^-(\varphi)$ as follows:
		\begin{itemize}
			\item For every atomic formula $A$:\\
			$\mathcal S^+(A) = \{P_A(\vec z_A)\to A\}$\\$\mathcal S^-(A) = \{A\to P_A(\vec z_A)\}$
			\item For every conjunction or disjunction $\varphi\circ\psi$ with $\circ\in\{\wedge,\vee\}$:\\
			$\mathcal S^+(\varphi\circ\psi) = \{P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\to P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\}\cup \mathcal S^+(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\circ\psi) =\{P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\to P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\}\cup \mathcal S^-(\varphi)\cup \mathcal S^-(\psi)$
			\item For every implication $\varphi \to\psi$:\\
			$\mathcal S^+(\varphi\to\psi) = \{(P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\wedge P_{\varphi}(\vec z_\varphi))\to P_{\psi}(\vec z_\psi)\}\cup \mathcal S^-(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\to\psi)  = \{(P_{\varphi}(\vec z_\varphi)\to P_{\psi}(\vec z_\psi))\to P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\}\cup \mathcal S^+(\varphi)\cup \mathcal S^-(\psi)$
			\item For quantified formulas $Qx\varphi(x)$ with $Q\in \{\forall,\exists\}$:\\
			$\mathcal S^+(Qx\varphi(x)) = \{P_{Qx\varphi}(\vec z_{Qx\varphi})\to QxP_{\varphi}(\vec z_{\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^+(\varphi)\}$\\$\mathcal S^-(Qx\varphi(x))  = \{QxP_{\varphi}(\vec z_{\varphi})\to P_{Qx\varphi}(\vec z_{Qx\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^-(\varphi)\}$
		\end{itemize}
		%We further set $\mathcal S(\varphi) = \mathcal S^+(\varphi)\cup\mathcal S^-(\varphi)$.
	\end{definition}

	\begin{lemma}
		$\bigwedge S^+(\varphi)\wedge P_\varphi(\vec z_\varphi)\to\varphi$ and $\bigwedge S^-(\varphi)\wedge \varphi\to P_\varphi(\vec z_\varphi)$ are valid both classically and intuitionistically.
	\end{lemma}

	It is straight-forward to extend structures to the additional symbols such that the formulas $S^+(\varphi)\cup\mathcal S^-(\varphi)$ are satisfied.
	\begin{definition}
		For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms of the form $P_\psi$. By slight abuse of notation we denote with $\vec z_\psi$ elements of the domain instead of variables. In the classical case, we set
		$$\begin{matrix}
			P_A^I(\vec z_A):\Leftrightarrow A^I(\vec z_A)\\
			P_{\varphi\wedge\psi}^I(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\wedge P_{\psi}^I(\vec z_\psi)\indent P_{\varphi\vee\psi}^I(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\vee P_{\psi}^I((\vec z_\psi))\\P_{\varphi\to\psi}^I(\vec z_{\varphi\to\psi}) :\Leftrightarrow (\neg P_{\varphi}^I(\vec z_{\varphi}))\vee P_{\psi}^I(\vec z_{\psi})\\P_{\forall x\varphi}^I(\vec z_{\forall x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for all $x\in M$}\}\indent P_{\exists x\varphi}^I(\vec z_{\exists x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for some $x\in M$}\},
		\end{matrix}$$
		and for intuitionistic logic and each world $u$, we set
		$$\begin{matrix}
			P_A^{I_u}(\vec z_A):\Leftrightarrow A^{I_u}(\vec z_A)\\
			P_{\varphi\wedge\psi}^{I_u}(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\wedge P_{\psi}^{I_u}(\vec z_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\vee P_{\psi}^{I_u}((\vec z_\psi))\\
			P_{\varphi\to\psi}^{I_u}(\vec z_{\varphi\to\psi}) :\Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec z_{\varphi}))\vee P_{\psi}^{I_w}(\vec z_{\psi})\text{ for all $w\geq u$}\\
			P_{\forall x\varphi}^{I_u}(\vec z_{\forall x\varphi}) :\Leftrightarrow P_{\varphi}^{I_w}(\vec z_\varphi) \text{ for all $w\geq u$, $x\in M_w$}\indent P_{\exists x\varphi}^{I_u}(\vec z_{\exists x\varphi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi) \text{ for some $x\in M_u$}.
		\end{matrix}$$
	\end{definition}
	From this definition we directly obtain the following Lemmata by induction on the formula height.
	\begin{lemma}\label{thm:struct1}
		For every formula $\varphi$ and structure $\mathcal M$, we have that $\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$.
	\end{lemma}

	\begin{lemma}\label{thm:struct2}
		For every structure $\mathcal M$,
		$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi(\vec z_\varphi)$.
	\end{lemma}

	Then from the previous three Lemmata we get:

	\begin{corollary}\label{eequivalid}
		In both intuitionistic and classical logic
		\begin{itemize}
			\item $\varphi$ is satisfiable iff $\mathcal \bigwedge S^+(\varphi)\wedge P_\varphi(\vec z_\varphi)$ is, and
			\item $\varphi$ is valid iff $\bigwedge\mathcal S^-(\varphi)\to P_\varphi(\vec z_\varphi)$ is.
		\end{itemize}
	\end{corollary}
